---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The data exists in the cloned directory, we get the data from a function:

```{r}
get.data <- function() {
    zipfile <- "./activity.zip"
    if (! file.exists("./activity.csv")) {
      stopifnot(file.exists(zipfile))
      unzip(zipfile)
    }
    activity <- read.delim(file = "./activity.csv", header = TRUE, sep = ",")
    activity$date <- as.Date(activity$date)
    activity
}

activity <- get.data()
```

In the rest of the code, I use several times the following functions:

```{r}
remove_na <- function(A) { A[complete.cases(A), ] }

is.weekday <- function(day) {
    weekdays(day) %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
}
```




## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
